---
title: "NYTBestsellers_data_vis"
author: "Uday Gadge"
date: "2023-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Reading the data


```{r}
library(dplyr)
library(ggplot2)
library(readr)

path <- "C:/Users/gadge/OneDrive/Desktop/MachineLearning/Project/Data/NYTimes_Bestsellers_raw_data"

df <- read_csv(paste(path,"/NYTimesBestsellers_clean_data.csv",sep = ""))
head(df)
```

Color codes to be used in the project


```{r}
#color codes
red <- '#740001'
gold <- '#D3A625'
  
blue <- '#0E1A40'
bronze <- '#946B2D'
  
yellow <- '#FFD800'
black <- '#000000'
  
green <- '#1A472A'
silver <- '#5D5D5D'
  
```


```{r}
unique(df$genre)
```

top 10 authors as per number of distinct books on the list


```{r}
library(dplyr)
library(ggplot2)

df %>% group_by(primary_author) %>% summarise(books = n_distinct(title)) %>% top_n(10) %>%
  ggplot(aes(x = books,y = reorder(primary_author,books))) + 
  geom_bar(stat = 'identity', fill = '#740001', color = '#D3A625') + 
  geom_text(aes(label = books), hjust = 1.6, color = '#D3A625') +
  xlab("Books") +
  ylab("Authors") +
  theme_minimal()
```

Simplifying the genres


```{r}
Fiction <- c("combined-print-and-e-book-fiction","hardcover-fiction",
             "trade-fiction-paperback")
Non_Fiction <- c("combined-print-and-e-book-nonfiction","hardcover-nonfiction",
                 "paperback-nonfiction")
Advice <- c("advice-how-to-and-miscellaneous")   
Young_adult <- c("young-adult-hardcover")
```

```{r}
genre_simplified <- function(genre) {
  if (genre %in% Fiction){result <- "Fiction"}
  if (genre %in% Non_Fiction) {result <- "NonFiction"}
  if (genre %in% Advice) {result <- "Advice"}
  if (genre %in% Young_adult) {result <- "YoungAdult"}
  return(result)
}
df$genre_modified <- sapply(df$genre, genre_simplified)
```
```{r}
head(df)
```


top 10 authors as per number of distinct books on the list for every genre



```{r}
df %>% group_by(genre_modified,primary_author) %>% 
  summarise(books = n_distinct(title)) %>% 
  arrange(desc(books)) %>% group_by(genre_modified) %>%
  slice(1:10) %>%
  ggplot(aes(x = books,y = reorder(primary_author,books))) + 
  geom_bar(stat = 'identity', fill = '#0E1A40', color = '#946B2D') + 
  geom_text(aes(label = books), hjust = 1.6, color = '#946B2D') +
  xlab("Books") +
  ylab("Authors") +
  theme_minimal() + facet_wrap(~genre_modified, scales = 'free')
```

Top 10 books as per total weeks on different lists.


```{r}
df %>% group_by(title, genre, genre_modified) %>% summarize(weeks = max(weeks_on_list)) %>%
  group_by(title) %>% summarize(total_weeks = sum(weeks)) %>% top_n(10) %>%
  ggplot(aes(x = total_weeks,y = reorder(title,total_weeks))) + 
  geom_bar(stat = 'identity', fill = '#FFD800', color = '#000000') + 
  geom_text(aes(label = total_weeks), hjust = 1.6, color = '#000000') +
  xlab("Total Weeks on list") +
  ylab("Book") +
  theme_minimal() 
```


Top 10 books as per weeks on list for every genre.


```{r}
df %>% group_by(title, genre, genre_modified) %>% summarize(weeks = max(weeks_on_list)) %>%
  group_by(title, genre_modified) %>% summarize(total_weeks = sum(weeks)) %>%
  arrange(desc(total_weeks)) %>%
  group_by(genre_modified) %>%
  slice(1:10) %>% 
  ggplot(aes(x = total_weeks,y = reorder(title,total_weeks))) + 
  geom_bar(stat = 'identity', fill = '#1A472A', color = '#5D5D5D') + 
  geom_text(aes(label = total_weeks), hjust = 1.6, color = '#5D5D5D') +
  xlab("Total Weeks on list") +
  ylab("Book") +
  theme_minimal() + facet_wrap(~genre_modified, scales = 'free')
```
```{r}
colnames(df)

```


Distribution of years since published for every genre



```{r}
df %>% filter(!is.na(Age_book)) %>% select(title, genre_modified, Age_book) %>%
  group_by(title,genre_modified, Age_book) %>% slice(1) %>%
  ggplot(aes(x = genre_modified, y = Age_book, fill = genre_modified)) + geom_boxplot()+
  scale_fill_manual(values = c("Fiction" = '#740001',
                                 "NonFiction" = '#0E1A40',
                                 "Advice" = '#FFD800',
                                 "YoungAdult" = '#1A472A'))+
  xlab("Genre") + ylab("Years since original Publication")
```


Distribution of years since published for every genre along with the weeks on list



```{r}
df %>% filter(!is.na(Age_book))%>%
  group_by(title, genre, genre_modified,Age_book)%>%
  summarize(weeks = max(weeks_on_list)) %>%
  group_by(title,Age_book, genre_modified) %>% 
  summarize(total_weeks = sum(weeks)) %>%
  ggplot(aes(x = genre_modified, y = Age_book, size = total_weeks)) +
  geom_point(aes(color = genre_modified),alpha = 0.3)+
  guides(color = FALSE) +
  xlab("Genre") + ylab("Years since the original Publication") +
  scale_size_continuous(range = c(2,10))+
  scale_colour_manual(values = c("Fiction" = '#740001',
                                 "NonFiction" = '#0E1A40',
                                 "Advice" = '#FFD800',
                                 "YoungAdult" = '#1A472A'))
```

Distribution of Age of Authors when they wrote the book for every genre.


```{r}
df %>% filter(!is.na(Age_author)) %>% select(title, genre_modified, Age_author) %>%
  group_by(title,genre_modified, Age_author) %>% slice(1) %>%
  ggplot(aes(x = genre_modified, y = Age_author, fill = genre_modified)) + geom_boxplot()+
  scale_fill_manual(values = c("Fiction" = '#D3A625',
                                 "NonFiction" = '#946B2D',
                                 "Advice" = '#000000',
                                 "YoungAdult" = '#5D5D5D'))+
  xlab("Genre") + ylab("Age of the Author When they wrote the book")
```

Distribution of Age of Authors when they wrote the book for every genre along with weeks on list.



```{r}
df %>% filter(!is.na(Age_author))%>%
  group_by(title, genre, genre_modified,Age_author)%>%
  summarize(weeks = max(weeks_on_list)) %>%
  group_by(title,Age_author, genre_modified) %>% 
  summarize(total_weeks = sum(weeks)) %>%
  ggplot(aes(x = genre_modified, y = Age_author, size = total_weeks)) +
  geom_point(aes(color = genre_modified),alpha = 0.5)+
  guides(color = FALSE) +
  xlab("Genre") + ylab("Age of the Author When they wrote the book") +
  scale_size_continuous(range = c(2,10))+
  scale_colour_manual(values = c("Fiction" = '#D3A625',
                                 "NonFiction" = '#946B2D',
                                 "Advice" = '#000000',
                                 "YoungAdult" = '#5D5D5D'))
```

Getting top 10 fiction books based on weeks on list


```{r}
df %>% group_by(title, genre, genre_modified) %>% summarize(weeks = max(weeks_on_list)) %>%
  group_by(title, genre_modified) %>% summarize(total_weeks = sum(weeks)) %>%
  arrange(desc(total_weeks)) %>%
  group_by(genre_modified) %>%
  slice(1:10) %>% filter(genre_modified == "Fiction") %>% select('title')
```

The Ranking history of these books.


```{r}
fiction_titles <- c('WHERE THE CRAWDADS SING'
,'MILK AND HONEY'
,'THE SILENT PATIENT'
,'THE SEVEN HUSBANDS OF EVELYN HUGO'
,'ALL THE LIGHT WE CANNOT SEE'
,'IT ENDS WITH US'
,'LITTLE FIRES EVERYWHERE'		
,'THE MIDNIGHT LIBRARY'
,'A MAN CALLED OVE')
df %>% filter(title %in% fiction_titles) %>% 
  ggplot(aes(x = published_date, y = rank, color = genre)) +
  geom_point() + geom_line() +
  scale_colour_manual(values = c( '#740001', '#0E1A40', '#FFD800','#1A472A')) +
  facet_wrap(~title) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Similarly for non fiction.

```{r}
df %>% group_by(title, genre, genre_modified) %>% summarize(weeks = max(weeks_on_list)) %>%
  group_by(title, genre_modified) %>% summarize(total_weeks = sum(weeks)) %>%
  arrange(desc(total_weeks)) %>%
  group_by(genre_modified) %>%
  slice(1:10) %>% filter(genre_modified == "NonFiction") %>% select('title')

```




```{r}
nonfiction_titles <- c('THE GLASS CASTLE'			
,'OUTLIERS'
,'THE DEVIL IN THE WHITE CITY'		
,'THINKING, FAST AND SLOW'			
,'THE BODY KEEPS THE SCORE'			
,'JUST MERCY'			
,'EDUCATED'			
,'SAPIENS'			
,'BORN A CRIME')

df %>% filter(title %in% nonfiction_titles) %>% 
  ggplot(aes(x = published_date, y = rank, color = genre)) +
  geom_point() + geom_line() +
  scale_colour_manual(values = c( '#D3A625', '#946B2D', '#000000','#5D5D5D')) +
  facet_wrap(~title) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

